# Data transformation

Because Quandl data is already cleaned and organized, all the data we use are simply put together in a function below. 

```{r}

countries_list =c("USA","CHN","JPN","DEU","IND","GBR","FRA","ITA","BRA","CAN","RUS","KOR","AUS","ESP","MEX","IDN","SAU","TUR","CHF")
```
We decided to check the cumulative CO2 emissions of top 20 countries with the highest GDP to see which of these countries emitted the largest amount of CO2.

The following function get_data_from_api reads the data from Quandl API into R.
```{r,echo=TRUE}

get_data_from_api <- function(url,cc)
{
  cc_url =paste(url,cc,sep="_")
  r = Quandl.datatable('WB/DATA', series_id=url, country_code=cc)
  return (r)
}
  
```


The get_all_data binds a list of interested data features and country codes and returns a table of all the data needed for the plots.

```{r,echo=TRUE}
get_all_data <-function(countries,data_names)
{
  table = data.frame()
  for (dn_tuple in data_names)
  {
    dn = dn_tuple[1]
    dt = dn_tuple[2]
    # print(dn)
    # print(dt)
    for (cc in countries)
      {
        cc_data = get_data_from_api(dn,cc)
        cc_data["DataType"] = dt 
        table = rbind(table,cc_data)
    }
  }
  
  return (table)
}


```



